---
title: "Assignment B1"
author: "Li Ju"
date: "2023-10-30"
output: github_document
---

# Exercise 1 and 2: Make a Function and Document your Function

In this exercise, I will make a generic function that can group by a specific column and summarize statistics calculated for another specific column in the dataset. This idea came from my repeated **group_by() %>% summarise()** workflow in my mda project.

```{r}
library(dplyr)

#' @title Summarize a column by a group
#' @details This function groups the data by a specified column and calculates statistics for another specified column.
#' @param df The data we will manipulate.
#' @param group_col The column the data should be grouped by.
#' @param summary_col The column statistics should be calculated for.
#' @return A new data frame with the summarized statistics including the average, maximum and minimum of the summary column..
summarize_col_by_group <- function(df, group_col, summary_col) {
  result <- df %>%
    group_by(.data[[group_col]]) %>%
    filter(!all(is.na(.data[[summary_col]]))) %>%
    summarise(
      average = mean(.data[[summary_col]], na.rm = TRUE),
      max_value = max(.data[[summary_col]], na.rm = TRUE),
      min_value = min(.data[[summary_col]], na.rm = TRUE),
    )
  return(result)
}
```

# Exercise 3: Include examples

I will include two examples from my mda project. So first I will load library and I will add age column into my vancouver_trees dataset:
```{r}
library(datateachr)
vancouver_trees <- vancouver_trees %>%
  mutate(age = difftime(Sys.Date(), date_planted))
```

## Example 1:
```{r}
# Used the generic function to grab information around trees in different neighbourhoods including the average age of trees, the maximal age of trees and the minimal age of trees
vancouver_trees_summary_by_neighbourhood <- summarize_col_by_group(vancouver_trees, group_col = "neighbourhood_name", summary_col = "age")
vancouver_trees_summary_by_neighbourhood
```

## Example 2:

```{r}
# Used the generic function to grab information around trees grouped by different species including the average age of trees, the maximal age of trees and the minimal age of trees
vancouver_trees_summary_by_species <- summarize_col_by_group(vancouver_trees, group_col = "species_name", summary_col = "age")
vancouver_trees_summary_by_species
```


# Exercise 4: Test the Function

```{r}

```

